How to make an abridged life table and calculate life expectancy

### 2016-09-20 working_teaching_examples/how_to_abridged_life_table.Rmd
cleaned up age decomp fx

```{r calc_age_decomp}
age_decomp <- le_age_decomp(life.table.qm, life.table.cm, num.alive="l_x", interval.years.lived="L_x", accumulated.years.lived = "T_x")
age_decomp
#check:
sum(age_decomp$C_x)
age_decomp$Life_Expectancy_2[age_decomp$Ages ==0] - age_decomp$Life_Expectancy_1[age_decomp$Ages ==0]

#also compare to the decomposition if the data is entered in the reverse order:
age_decomp2 <- le_age_decomp(life.table.cm, life.table.qm, num.alive="l_x", interval.years.lived="L_x", accumulated.years.lived = "T_x")
age_decomp2
#check:
sum(age_decomp2$C_x)
age_decomp2$Life_Expectancy_2[age_decomp2$Ages ==0] - age_decomp2$Life_Expectancy_1[age_decomp2$Ages ==0]

>>>>

```{r calc_age_decomp}
age_decomp <- le_age_decomp(life.table.qm, life.table.cm)
age_decomp
#check:
sum(age_decomp$C_x)
age_decomp$Life_Expectancy_2[age_decomp$Ages ==0] - age_decomp$Life_Expectancy_1[age_decomp$Ages ==0]

#also compare to the decomposition if the data is entered in the reverse order:
age_decomp2 <- le_age_decomp(life.table.cm, life.table.qm)
age_decomp2
#check:
sum(age_decomp2$C_x)
age_decomp2$Life_Expectancy_2[age_decomp2$Ages ==0] - age_decomp2$Life_Expectancy_1[age_decomp2$Ages ==0]
